Methodology for Assessing the State of the Practice for Domain X

### 2020-10-15 StateOfPractice/Methodology/Methodology.tex
updated section 2 of Methodology

The following are research questions that we want to answer in order to assess the state of practice of research software in our chosen domain:

\begin{enumerate}
\item What are the artifacts that current software packages consist of? 
\item What tools are used by current software packages?
\item What principles, processes, and methodologies are used in the development of current software packages?
\item What are the pain points for developers working on SCS projects? What aspects of the existing processes, methodologies and tools do they consider could potentially be improved? What processes, methodologies and tools have they changed in order to reduce obstacles?
\item What are the actions of research software developers toward:\pmi{to do: reverse engineer from questions to developers; might remove or completely alter points below}
\begin{enumerate}
\item sustainability?\pmi{meeting discussion did consider removing this}
\item usability?
\item modifiability?
\end{enumerate} 
\item How does software designated as high quality by this methodology compare with top rated software by the community? \pmi{review}
\end{enumerate}

>>>>

The following are research questions that we want to answer to assess the state of practice of research software in our chosen domain:

\begin{enumerate}
\item What are the artifacts that current software packages consist of? 
\item What tools are used by current software packages?
\item What principles, processes, and methodologies are used in the development of current software packages?
\item What are the pain points for developers working on SCS projects? What aspects of the existing processes, methodologies and tools do they consider could potentially be improved? What processes, methodologies and tools have they changed to reduce obstacles?
\item For research software developers, what specific actions are taken to address the following:\pmi{to do: reverse engineer from questions to developers; might remove or completely alter points below}\pmi{removed attitudes as per meeting discussion}
\begin{enumerate}
\item sustainability?\pmi{meeting discussion did consider removing this}
\item usability?
\item modifiability?\pmi{SS comment in issue 57: I think we want to keep modifiability in the list. The reasons you have listed are good reasons. Also, modifiability is such an important software quality, especially when it comes to having a good software development process.}
\end{enumerate} 
\item How does software designated as high quality by this methodology compare with top rated software by the community? \pmi{review}
\end{enumerate}
